\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2016-01-20 paper.tex
added comment
Mark me as affiliated with Microsoft since most of my work was done there.
updates
updates towards camera ready
State that part of the work was done while interning at Microsoft.
The paper is now over length.  If necessary, I can remove material
later to fix that.

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

\usepackage{color}
\definecolor{light-gray}{gray}{0.40}
\definecolor{orange}{rgb}{1,0.5,0}
%\newcommand{\SQComment}[1]{\textcolor{red}{Shaz: #1}}
%\newcommand{\PDComment}[1]{\textcolor{blue}{Pantazis: #1}}
%\newcommand{\MMComment}[1]{\textcolor{cyan}{Matt: #1}}
%\newcommand{\SCComment}[1]{\textcolor{magenta}{Shuo: #1}}
%\newcommand{\CHComment}[1]{\textcolor{blue}{Cheng: #1}}
\newcommand{\PTComment}[1]{\textcolor{orange}{Paul: #1}}

@@

%for single author (just remove % characters)
\author{
%{\rm Submission ID: \#127}} % end author
{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$}\\
{\rm Alastair F. Donaldson$^\dagger$, John Erickson$^\star$, Cheng Huang$^\star$, Akash Lal$^\star$}\\
{\rm Rashmi Mudduluru$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\star$}\\\\
$^\dagger$Imperial College London, $^\diamond$Massachusetts Institute of Technology, $^\star$Microsoft\\
} % end author

\maketitle

@@

>>>>

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\newcommand{\smark}{\ding{72}}

\usepackage{color}
\definecolor{light-gray}{gray}{0.40}
\definecolor{orange}{rgb}{1,0.5,0}
%\newcommand{\SQComment}[1]{\textcolor{red}{Shaz: #1}}
\newcommand{\PDComment}[1]{\textcolor{blue}{Pantazis: #1}}
%\newcommand{\MMComment}[1]{\textcolor{cyan}{Matt: #1}}
%\newcommand{\SCComment}[1]{\textcolor{magenta}{Shuo: #1}}
%\newcommand{\CHComment}[1]{\textcolor{blue}{Cheng: #1}}
\newcommand{\PTComment}[1]{\textcolor{orange}{Paul: #1}}

@@

%for single author (just remove % characters)
\author{
%{\rm Submission ID: \#127}} % end author
{\rm Pantazis Deligiannis$^{\dagger1}$, Matt McCutchen$^{\diamond1}$, Paul Thomson$^\dagger$, Shuo Chen$^\star$}\\
{\rm Alastair F. Donaldson$^\dagger$, John Erickson$^\star$, Cheng Huang$^\star$, Akash Lal$^\star$}\\
{\rm Rashmi Mudduluru$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\star$}\\\\
$^\dagger$Imperial College London, $^\diamond$Massachusetts Institute of Technology, $^\star$Microsoft\\
} % end author
\maketitle

@@

\stepcounter{footnote}
\footnotetext{Part of the work of these authors was done while they interned at Microsoft.}
